---
title: "MyLeafletPage"
author: "Dongying"
date: "9/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Project Instruction

Create a web page using R Markdown that features a map created with Leaflet.  

Host your webpage on either GitHub Pages, RPubs, or NeoCities.  

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!  

# My Leaflet Page: Dreaming camping site

It's already fall season, come outside for some adventure. Don't forget to bring your sleeping bags and your camera!

```{r cars}
library(leaflet)
my_map <- leaflet() %>% addTiles() %>% 
        addMarkers(lat=44.3386, lng= -68.2733, popup="Acadia National Park") %>% 
        addMarkers(lat=44.1486, lng= -71.4530, popup="Whit Mountain National Forest") %>% 
        addMarkers(lat=41.7200, lng= -74.2840, popup="Minnewaska State Park Preserve") %>% 
        addMarkers(lat=38.4755, lng= -78.4535, popup="Shenandoah National Park") %>% 
        addMarkers(lat=24.6285, lng= -82.8732, popup="Dry Tortugas National Park") %>% 
        addMarkers(lat=33.8734, lng= -115.9010, popup="Joshua Tree National Park")
my_map
```
